\paragraph{\Large Acknowledgements\\[0.5cm]}
{I am deeply honored and humbled to have had the privilege of pursuing my doctoral degree at the prestigious Massachusetts Institute of Technology (MIT). The unwavering support, invaluable guidance, and exceptional mentorship of the esteemed faculty have been instrumental in shaping the trajectory and success of this research.

At the forefront of my gratitude stands Professor Dr. Andrew Ng, whose visionary leadership and unparalleled expertise have been a constant source of inspiration throughout my academic journey. His insightful feedback, unwavering encouragement, and commitment to propelling the boundaries of knowledge have been truly transformative. Under his tutelage, I have not only honed my technical prowess but have also developed a profound appreciation for the power of innovation and the pursuit of groundbreaking discoveries.

The vibrant and collaborative environment fostered by the MIT community has been instrumental in fueling my intellectual growth and fostering a deep sense of camaraderie. The university's renowned laboratories, cutting-edge resources, and world-class facilities have provided an unparalleled platform for my research endeavors, enabling me to push the limits of what is possible in the field of computer science.

I am immensely grateful to the United States government for the generous doctoral fellowship that has made this journey possible. The financial support and access to research opportunities have been pivotal in allowing me to delve deeply into the complexities of my chosen field and contribute meaningfully to the advancement of knowledge.

Furthermore, I extend my heartfelt appreciation to the tech giants Google and Meta for their invaluable sponsorship and collaborative support. Their willingness to share their state-of-the-art technologies, computing infrastructure, and technical expertise has been instrumental in shaping the direction and depth of my research. The synergistic partnership between academia and industry has been a driving force in propelling my work forward and ensuring its real-world relevance and impact.

As I reflect on this remarkable chapter of my life, I am filled with a deep sense of gratitude and a renewed commitment to leveraging the knowledge and skills I have acquired to make a meaningful difference in the world. I am truly honored to have been entrusted with this opportunity, and I pledge to continue pushing the boundaries of innovation and discovery, inspired by the unwavering support and guidance of this esteemed community.
}


\hfill
\begin{minipage}[t]{0.5\textwidth}\raggedright
Best regards,\\
Thanh Pham
\end{minipage}
